\documentclass[../../projectPlan.tex]{subfiles}

\begin{document}

	\chapter{Project Tasks and Schedule}	
	
		In this chapter is described how the work is divided and organized. For each part of this project we make a brief description, we report the deadline date and what team member is assigned to that part. Our team is composed of two members, Simone Deola and Davide Cremona.
		Parts of the project:
		\begin{itemize}
		\item \textbf{RASD and Project Plan}: In this part the team produce a first release of the Requirements Analysis and Specification Document an a Project Plan Document in which it is described the project and the team make an estimation of what it will be done and when it will be done. We specify that this two documents are only the first releases because they can be changed on the future steps. The two documents can be done in parallel or consequentially.
		\begin{itemize}
		\item Estimate starting time: 10/2015.
		\item Deadline:6/11/2015.
		\item Workers: Simone Deola, Davide Cremona.
		\end{itemize}
		
		
		\item \textbf{Design Document}: In this part the team produce a first release of the Design Document of the system. This document describe how the system is organized. So, in this phase the team start to determine the structure of the system and how the system works. We specify that this document are only the first release because it can be changed on the future steps.
		\begin{itemize}
		\item Estimate starting time: 7/11/2015.
		\item Deadline:4/12/2015.
		\item Workers: Simone Deola, Davide Cremona.
		\end{itemize}
		
		
		
		
		
		\item \textbf{Integration Test Plan Document}: In this part the team produce a first release of the Integration Test Plan Document. This document describe how to test the various part of the system. We specify that this document are only the first release because it can be changed on the future steps.
		\begin{itemize}
		\item Estimate starting time: 5/12/2015.
		\item Deadline:21/01/2016.
		\item Workers: Simone Deola, Davide Cremona.
		\end{itemize}		
		
		\item \textbf{Coding and Unity test}: At this point of the project we have described how the system is formed so each team member can take independent parts of the system and develop it. How to split the parts of the system will be more clear when the DD will be produced. The code that is developed on this part must be tested too, so each member must produce the unity test on the part that have produced. On this part the members can work in parallel since the documentation define all the interfaces and how they works. For example, Simone Deola can work on the Database and on the front end while Davide Cremona works on the back end part (if the structure of the system will be defined in this way).
		\begin{itemize}
		\item Estimate starting time: 22/01/2016.
		\item Deadline:22/06/2016.
		\item Workers: Simone Deola, Davide Cremona.
		\end{itemize}
		
		
		\item \textbf{Integration and Test Phase}: In this phase of the project the team integrate all the part of the system, developed and tested in the previous phase, and test how it works when putted together. On this phase the team release also the integration tests. The step of the integration and the relative tests will be described on the ITPD. On this phase the two members of the team will work together.
		\begin{itemize}
		\item Estimate starting time: 23/06/2016.
		\item Deadline:31/07/2016.
		\item Workers: Simone Deola, Davide Cremona.
		\end{itemize}
		
		\item \textbf{Implementation}: In this phase the team makes the various Performance Test of the system. After this step the system is ready to be released.
		\begin{itemize}
		\item Estimate starting time: 01/08/2016.
		\item Deadline:30/08/2016.
		\item Workers: Simone Deola, Davide Cremona.
		\end{itemize}
		
		
		
		
		\end{itemize}
		 
		

		

\end{document}