\subsection{Software System Attributes}
These are the quality-attributes used to evaluate the performance of myTaxiService system.

	\subsubsection{Adaptibility}
	The developed system must be adaptable to other Software Engineering cycles (beacuse of updates or revisions). To accomplish this goal, it must be developed following the major software design patterns like MVC. Using these design patterns, the system is more adaptable for example in the case of adding some users types or database entities.

	\subsubsection{Availability}
	The system must be available every time, so it must be hosted into cloud platforms and maybe even in the backup server farm to ensure data redundancy.

	\subsubsection{Compatibility}
	Given that the mobile applications are developed in the natives programming languages of the various operative systems, the web application must be compatible (in style and functioning) with the major browsers listed in the \hyperref[tab:browsersTable]{Browsers Table}.

	\subsubsection{Fault-Tolerance}
	The system should not crash or get into infinite loops in waiting for user response. To ensure this goal, for every message that will be sent to an user, there will be a Timer-Thread that will be waiting for a limited amount of time and after that the system will have to consider the user disconnected

	\subsubsection{Maintainability}
	The system should be maintanable over time to perform updates or add new features. To accomplish this goal, the code must be properly documented even if there are no public API.

	\subsubsection{Modularity}
	To ensure more maintainability, the system must be developed in a modular way. Every functionality must should depend as least as possible by the others and to do this it's recommended using software design patterns to develop the system.

	\subsubsection{Portability}
	The server side of the system must be portable through different server operating systems and to do this it will be necessary to not use proprietary programming languages.

	\subsubsection{Simplicity}
	The applicaton should be simple and accessible to novice users. To ensure this goal, the application interface must be as simple as possible and the main functions has to be directly accessible from the homepage.