\chapter{Overall Description}
	
	\section{Product perspective}
	The system will be composed of a web application and a mobile application developed for the three major OS ( Apple iOS, Android, Windows 10). The system will provide some API with the purpose of a future connection with another travel planning systems. 
		
	\section{User Characteristics}
	% this user here is ok and don't have to be hyperreferred
	We suppose that there are two types of users that will use our system. The first type is composed of who want to find a taxi for a travel in the simplest way (\hyperref[sec:customer]{customers}). They must be able to access to a web browser or download and using a mobile application. The second one is composed of \hyperref[sec:tdriver]{taxi drivers}, who want to increment their productivity. In addiction to being able to access to a web browser or downloading and using our mobile application, they must have a taxi license.
		
	\section{Constrains}
		
		\subsection{Regulatory Policies}
		myTaxiService  has to meet regulatory policies about taxis in the countries where it will be used.

		\subsection{Hardware Limitations}
		The only hardware limitation that the myTaxiService mobile application has to meet is the mobile phones characteristics. the rest of the 			system will not be affected by particular hardware limitations.

		\subsection{Software Limitations}
		myTaxiService mobile application has to be compatible with all major mobile operating systems (Android, Apple iOS, Windows 10).
		Moreover, myTaxiService web application has to be compatible with all major browsers (Chrome, Safari, Firefox, Microsoft Edge).

		\subsection{Parallel Operations}
		Our system must be able to perform parallel operations on the database to satisfy all the requests from multiple users.

		\subsection{Documents Related}

			\begin{itemize}
				\item Requirements and Analysis Specification Document (RASD)

				\item Design Document (DD)
			\end{itemize}

	\section{Assumptions}

			\begin{itemize}
				\item Every \hyperref[sec:tdriver]{taxi driver} has equipped a smartphone during working hours.

				\item Every \hyperref[sec:tdriver]{taxi driver} has a unique taxi license.

				\item Every taxi has a GPS locator to send GPS information to the central server.

				\item Android, Apple iOS or Windows 10 are available on the \hyperref[sec:ruser]{registered users} smartphones.

				\item Every \hyperref[sec:ruser]{registered users} can connect to the Internet with a mobile device when outside.

				\item When a \hyperref[sec:customer]{customer} require a taxi, the GPS information about his location are automatically sent to the central server.

				\item The reservation of a ride is made at least two hours before the ride.

				\item The deletion of a reservation is made at least two hours before the ride.

				\item The requests of the \hyperref[sec:customer]{customers} are automatically notified to the first \hyperref[sec:tdriver]{taxi driver} in the zone queue.

				\item If a \hyperref[sec:tdriver]{taxi driver} declines a request he will be placed in the bottom of the zone queue.

				\item If a request is declined it will be forwarded to the next \hyperref[sec:tdriver]{taxi driver} in the zone queue.

				\item If a \hyperref[sec:customer]{customer} makes a bad use of the taxi request system, he can be reported as a bad \hyperref[sec:customer]{customer}.

				\item If a \hyperref[sec:tdriver]{taxi driver} notifies his availability, it is because he is actually avaiable

				\item If a \hyperref[sec:tdriver]{taxi driver} notifies his availability, it is because he wants to be notified of \hyperref[sec:customer]{customers} that needs a ride.

				\item If a \hyperref[sec:tdriver]{taxi driver} accepts a request, the requesting \hyperref[sec:customer]{customer} will be notified
			\end{itemize}

	\section{Future possible Implementations}
	A possible future implementation can be a complex feedback system, that allows the \hyperref[sec:customer]{customers} to leave a comment about the \hyperref[sec:tdriver]{taxi driver} and vice versa.
	For example, \hyperref[sec:tdriver]{taxi drivers} can be interested in knowing the punctuality or the behaviour of the \hyperref[sec:customer]{customer} who requests the ride.